Formalization of Abstract Rewriting

### 2025-02-22 Relations/Paper/Definitions.tex
Progress throughout report

\section{Definitions}
\label{sec:Definitions}

The following definitions are provided to ensure clarity and precision
in our discussion.
 When useful, we also include the name and type of
definition as we have implemented it in Agda, allowing the report to guide the code
and vice versa.

@@

In the context of abstract rewriting, we will often write $a \rstep_R b$
in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
$a \bstep b$ for $(b,a) \in R$.  When the relation $R$ is clear from the context,
we may drop the corresponding subscript.

We first define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.

\begin{definition}  Let $A$ and $R$ be as above, and let $a \in A$.
  \begin{description}
    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[$a \in SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
  \end{description}

    An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
    via multi-step relations to some common reduct.

    A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
    via multi-step relations to some common reduct.
    A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
\end{definition}

@@

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.

    A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.

    A relation $R$ is strongly normalizing (SN) if every
    $a \in A$ is $R$-strongly normalizing.
\end{definition}

@@

\begin{definition}
    An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and
    $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.

    A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.
\end{definition}

\begin{definition}
    The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
\end{definition}

\begin{definition}
An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
$a \estep b$  $\implies$
$a \mstep b$, for any normal form $b \in A$.

A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
\end{definition}

In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.

In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
\begin{definition}
An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
$a \estep b$  $\implies$
$a \equiv b$, for any normal form $b \in A$.

A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
\end{definition}

\begin{definition}
An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
$b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.

A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
$R$-unique normal form property with respect to reduction.
\end{definition}
In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen
in counterexample (\sacomment{TODO: put counterexample here when section is complete}).

@@

\begin{definition}
    An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
\end{definition}

Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda
function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).

@@

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.

    A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
    from $a$ is also strongly minimal.

    A relation $R$ is strongly minimal (SM) if every
    $a \in A$ is $R$-strongly minimal.
\end{definition}

\begin{definition}
   An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
   $a \mstep b$ and $a \mstep c$  $\implies$
   $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.

   A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
\end{definition}
\begin{definition}
    \label{d:inc}
    A relation $R \sse A \times A$ is called \emph{increasing} if there
    exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
    \[ Rxy \to |x| < |y| \]
\end{definition}

>>>>

\section{Definitions}
\label{sec:Definitions}
\sacomment{Need to update move from WNFP to NP, WMFP to MP, NP to NP\_0}
\sacomment{Need to update to refer to macros for properties}
The following definitions are provided to ensure clarity and precision
in our discussion.
 When useful, we also include the name and type of
definition as we have implemented it in Agda, allowing the report to guide the code
and vice versa.

@@

In the context of abstract rewriting, we will often write $a \rstep b$
in place of $(a,b) \in R$.  Similarly, we will write $a \mstep b$ for $(a,b) \in R^*$,
$a \bstep b$ for $(b,a) \in R$.  When the relation $R$ is clear from the context,
we may drop the corresponding subscript.

We next define rewriting-theoretic concepts like confluence and normalization relative to a fixed element of $A$; global versions of these properties are obtained by universal quantification.
For equivalent definitions, see \texttt{ARS-Properties.agda}.

\begin{definition} The following definitions relate to normalization. Let $A$ and $R$ be as above, and let $a \in A$.
  \begin{description}
    \item[$a \in \NF_R$] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$ 
    \item[$a \in \WN_R$] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[$a \in \SN_R$]  \emph{$a$ is $R$-accessible}, see Definition \ref{d:WFacc}.
  \end{description}
\end{definition}

\begin{definition} The folowing definitions relate to being minimal. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \MF_R$] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[$a \in \WM_R$] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[$a \in \SM_R$]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$ or every element one $R$ step from $a$ is also strongly minimalizing.
    \end{description}
\end{definition}
We found that there was a strong interrelationship between the normalizing properties and the minimal properties. This relationship is 
captured in Figure \ref{fig:norm-hierarchy}.

\begin{figure}[h]   
    \centering
        \begin{tikzpicture}[auto,
            arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
            % A box style
            \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]   
            % Define the nodes
            \node (SN) [boxnode] at (4,0) {$\SN$};
            \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
            \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
            \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};

            % Draw the arrows to form a diamond
            \draw [arrowstyle] (SN) -- (WN);
            \draw [arrowstyle] (SN) -- (SR);
            \draw [arrowstyle] (WN) -- (WR);
            \draw [arrowstyle] (SR) -- (WR);
        \end{tikzpicture}
        \caption{A hierarchy of normalizing and minimal properties.}
        \label{fig:norm-hierarchy}
\end{figure}

The implications will be explored in detail in Section \ref{sec:Implications}.

A trivial implication not captured in the above figure is covered in Proposition \ref{prop:nftomf}. 
\begin{proposition}\label{prop:nftomf}
    $a\in NF_R \implies a \in MF_R$ 
\end{proposition}    
\begin{proof}
    See, \verb|NF ⊆ MF : ∀x → NFx → MFx| in \texttt{ARS-Implications.agda}.
\end{proof}

\begin{definition} The following definitions relate to confluence. Let $A$ and $R$ be as above, and let $a \in A$.
    \begin{description}
        \item[$a \in \WCR_R$] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \CR_R$] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
        \item[$a \in \NPe_R$] \emph{$a$ has the equivalence normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
        \item[$a \in \NP_R$] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$\footnote{In \terese $\NF$ is used to denote $\NPe$, whereas we have chosen to use $\NF$ to denote normal form.}. 
        \item[$a \in \MP_R$] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
        \item[$a \in \UN_R$] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in NF$.
        \item[$a \in \UNto_R$] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in NF$.
    \end{description}
\end{definition}

Again, we found that there was a strong interrelationship between the properties, captured in Figure \ref{fig:conf-hierarchy}, which are explored in Section \ref{sec:Implications}.

\begin{figure}[h] 
    \centering

        \begin{tikzpicture}[auto,
          arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
          % A box style
          \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]

          % Place the nodes vertically (top to bottom)
          \node (Confluent) [boxnode] at (-4,0) {$\CR$};
          \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
          \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
          \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};

          % Draw arrows downwards
          \draw[arrowstyle] (Confluent) -- (RP);
          \draw[arrowstyle] (RP) -- (WN);
          \draw[arrowstyle] (WN) -- (UN);

          \end{tikzpicture}
          \caption{A hierarchy of confluent properties.}
          \label{fig:conf-hierarchy}

\end{figure}

\sacomment{Make sure somewhere it is mentioned that NP equals $NP_=$ and that UN does not equal UNto.}

\sacomment{Work for Saturday: Get the final definitions written up: namely the RP definitions and maybe make a figure to show those interrelationships}.
%     \begin{definition}

%   An element $a \in A$ is \emph{R-weakly confluent} ($WCR_R$) if all single step relations from $a$ can always converge
%     via multi-step relations to some common reduct.

%     A relation $R$ is \emph{weakly confluent} (AKA weakly Church-Rosser (WCR)) if every $a \in A$ is R-weakly confluent.
% \end{definition}

% \begin{definition}
%     An element $a \in A$ is \emph{R-confluent} ($CR_R$) if all multi-step relations from $a$ can always converge
%     via multi-step relations to some common reduct.
%     A relation $R$ is \emph{confluent} (AKA Church-Rosser (CR)) if every $a \in A$ is R-confluent.
% \end{definition}

@@

% \begin{definition}
%     An element $a \in A$ is \emph{$R$-weakly normalizing} ($WN_{R}$)if $a \mstep b$ for some normal form $b \in A$.

%     A relation $R$ is weakly normalizing (WN) if every $a \in A$ is $R$- weakly normalizing.
% \end{definition}

% \begin{definition}
%     An element $a \in A$ is \emph{$R$-strongly normalizing} ($SN_R$) if every sequence of relations starting from $a$ is finite.

%     A relation $R$ is strongly normalizing (SN) if every
%     $a \in A$ is $R$-strongly normalizing.
% \end{definition}

@@

% \begin{definition}
%     An element $a \in A$ has the \emph{$R$-weak normal form property} ($WNFP_{R}$) if $a \mstep b$ and
%     $a \mstep c \implies c \mstep b$, for all $c \in A$ and all normal form $b \in A$.

%     A relation $R$ has the \emph{weak normal form property} (WNFP) if every $a \in A$ has the $R$-weak normal form property.
% \end{definition}

% \begin{definition}
%     The \emph{equivalence relation} of $R$ is the smallest relation $\estep$ that contains $R$ and is reflexive, transitive, and symmetric.
% \end{definition}

% \begin{definition}
% An element $a \in A$ has the \emph{$R$-normal form property} ($NFP_{R}$) if
% $a \estep b$  $\implies$
% $a \mstep b$, for any normal form $b \in A$.

% A relation $R$ has the \emph{normal form property} (NFP) if every $a \in A$ has the $R$-normal form property.
% \end{definition}

% In ARS-Implications.agda we show the equivalence of WNFP and NFP when applied globally in the function $\mathtt{NP \leftrightarrow WNFP}$.

% In the next definition we deonte two elements $a, b \in A$ being equivalent with $a \equiv b$.
% \begin{definition}
% An element $a \in A$ has the \emph{{R}-unique normal form property} ($UN_{R}$) if
% $a \estep b$  $\implies$
% $a \equiv b$, for any normal form $b \in A$.

% A relation $R$ has the \emph{unique normal form property} ($UN$) if every $a \in A$ has the $R$-unique normal form property.
% \end{definition}

% \begin{definition}
% An element $a \in A$ has the \emph{${R}$-unique normal form property with respect to reduction} ($UN^ \to _{R}$) if
% $b \bmstep  \cdot  \mstep c$  $\implies$ $b \equiv c$, for all normal forms $b,c \in A$.

% A relation $R$ has the \emph{unique normal form property with respect to reduction} ($UN^\to$) if every $a \in A$ has the
% $R$-unique normal form property with respect to reduction.
% \end{definition}
% In ARS-Implications.agda we show that $UN$ implies $UN\to$ but the inverse implication doesn't hold, as seen
% in counterexample (\sacomment{TODO: put counterexample here when section is complete}).

@@

% \begin{definition}
%     An element $a \in A$ has the \emph{minimal form property} ($MF$) if $a \mstep b \implies b \mstep a$ for all $b \in A$.
% \end{definition}

% Note that being a normal form is a trivial case of the minimal form property (as we prove in ARS-implications.agda
% function $\mathtt{NF\subseteq MF : \forall {x} \to NF x \to MF x}$).

@@

% \begin{definition}
%     An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.

%     A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
% \end{definition}

% \begin{definition}
%     An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
%     from $a$ is also strongly minimal.

%     A relation $R$ is strongly minimal (SM) if every
%     $a \in A$ is $R$-strongly minimal.
% \end{definition}

% \begin{definition}
%    An element $a \in A$ has the \emph{${R}$-weak minimal form property} ($WMFP_R$) if
%    $a \mstep b$ and $a \mstep c$  $\implies$
%    $c \mstep b$, for all $c \in A$ and all $b \in A$ with the minimal form property.

%    A relation $R$ has the \emph{weak minimal form property} (WMFP) if every $a \in A$ has the $R$-weak minimal form property.
% \end{definition}
\begin{definition}
    \label{d:inc}
    A relation $R \sse A \times A$ is called \emph{increasing} if there
    exists a ``size function'' $|-| : A \to \nat$ satisfying, for all $x, y \in A$,
    \[ Rxy \to |x| < |y| \]
\end{definition}

### 2025-02-22 Relations/Paper/Formalization.tex
Progress throughout report

\verb|RP-↔RP : R is RP- ↔ R is RP| \footnote{ARS-implications.agda}

Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
these proofs we found to rely on classical principles. The second proof was amenablbe to a 
constructive formalization which we carried out in the function

\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnote{ARS-NewmansLemma.agda}

We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
that we produce a new generalization of Newman's lemma. Every relation with the properties 
$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:

\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnote{ARS-NewmansLemma.agda}

and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnote{ARS-NewmansLemma.agda}

The formalization of the proof that $\WCR \land \WN \land \Inc \implies \SN$ proved particularly difficult. 
As already mentioned, we substituted out the property $\Inc$ for the property $\RP$ however 
we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnote{ARS-Theorems.agda}
The classical property $\decSN$ is a property that states it is decidable whether a given 
element has the property of being $\SN$. \sacomment{Should say more on this proof.}

>>>>

\verb|RP-↔RP : R is RP- ↔ R is RP| \footnotemark[1]
\footnotetext[1]{\texttt{ARS-implications.agda}}
Three proofs are given in \terese of Newman's Lemma (Theorem 1.2.1). The first and third of 
these proofs we found to rely on classical principles. The second proof was amenablbe to a 
constructive formalization which we carried out in the function

\verb|NewmansLemma : R isSN → R isWCR → R isCR| \footnotemark[2]
\footnotetext[2]{\texttt{ARS-NewmansLemma.agda}}
We show in section \ref{sec:Implications} that $\SN$ implies $\SM$, and it is from this implication 
that we produce a new generalization of Newman's lemma. Every relation with the properties 
$\SM$ and $\WCR$ has the property of $\CR$. This holds true both locally and globally as we show in:

\verb|LocalNewmansLemmaRecurrent : R isWCR → SM ⊆ CR| \footnotemark[2]

and \verb|GlobalNewmansLemmaRecurrent : R isWCR → R isSM → R isCR| \footnotemark[2]

The formalization of the proof that $\WCR \land \WN \land \Inc \implies \SN$ proved particularly difficult. 
As already mentioned, we substituted out the property $\Inc$ for the property $\RP$ however 
we found that we still require a classical principle in order for the proof to hold (as can be seen in the type of our proof):
\verb|iii : R isWN → R isWCR → R isRP- → dec (SN) → R isSN| \footnotemark[3] \footnotetext[3]{\texttt{ARS-Theorems.agda}}
The classical property $\decSN$ is a property that states it is decidable whether a given 
element has the property of being $\SN$. \sacomment{Should say more on this proof.}

### 2025-02-22 Relations/Paper/Implications.tex
Progress throughout report

@@

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.

@@

\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & CE, CE-       & $\CR$\footnotemark[1] , CE-          & $\CR$\footnotemark[1], CE            & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-     & $\CR$, CE-     & $\CR$, CE-        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}
\begin{table}[h!]
    \centering
    \caption{Global implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     & $\CR$, CE-        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

@@

@@

The tables show that there are two changes when moving from properties holding locally to globally. 
Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
globally but not locally.

>>>>

\newenvironment{counterexample}[1][]{%
    \refstepcounter{CEcounter} % Increment the counter
    \noindent \scriptsize\textbf{{\theCEcounter } }  #1\par
}

@@

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are shown below the tables in subsection \ref{subsec:counterexamples}.

@@

\sacomment{When the table and CE are finished, write an explanation that the CE to the local table 
assume local WCr and the global table CEs assume global WCR!}
\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-\ref{CE:4}, CE-\ref{CE:12}     & CE-\ref{CE:4}, CE-\ref{CE:7}       & CE-\ref{CE:4} , CE-\ref{CE:9}          & CE-\ref{CE:4}, CE-\ref{CE:4}            & $\CR$\footnotemark[1] , $\SN$ \\
    \hline
    $\NP$ & CE-\ref{CE:10},CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & CE-\ref{CE:11} , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}
\begin{table}[h!]
    \centering
    \caption{Global implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\NP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[1] , CE-\ref{CE:9}          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-\ref{CE:9}    & $\CR$, CE-\ref{CE:7}    & $\CR$\footnotemark[2] , CE-\ref{CE:9} & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-\ref{CE:9}     & $\CR$, CE-\ref{CE:7}     & $\CR$, CE-\ref{CE:9}        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

@@

\subsection{Counterexamples}\label{subsec:counterexamples}
% Setting up the ce counter 
\newcounter{CEcounter}
\renewcommand{\theCEcounter}{\arabic{CEcounter}}

    \begin{center}
        \begin{tabular}{ccc}  % Three columns per row
            % First Counterexample
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:1}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
            &
            % Second Counterexample
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:2}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        a & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
            &
            % Third Counterexample
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:3}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        a \arrow[loop left] & b \arrow[l] \arrow[r, bend left] & c \arrow[l, bend left] \arrow[r] & d \arrow[loop right]
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
            \\  % New row
            \\

            % Fourth Counterexample
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:4}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        & a \arrow[d] \arrow[dl] \\ e & b \arrow[l] \arrow[r] & c \arrow[r, bend left] & d \arrow[l, bend left]
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
            &
            % Fifth Counterexample
            % \begin{minipage}{0.3\textwidth}
            %     \centering
            %     \begin{counterexample}\label{CE:5}
            %         \begin{tikzcd}[row sep=small, column sep=small]
            %             d & a \arrow[l, two heads] \arrow[r, two heads] & b \arrow[r, bend left] & c \arrow[l, bend left]
            %         \end{tikzcd} \\
            %     \end{counterexample}
            % \end{minipage}

            % Sixth Counterexample - This one shows why UN -> doesn't imply UN
            \begin{minipage}{0.3\textwidth}
                \centering
                \begin{counterexample}\label{CE:un}
                    \begin{tikzcd}[row sep=small, column sep=small]
                        n & c \arrow[l] \arrow[r] & a \arrow[r, bend left] & b \arrow[l, bend left]
                        & d \arrow[l] \arrow[r] & m
                    \end{tikzcd} \\
                \end{counterexample}
            \end{minipage}
        % \\ % New row
        % \\
        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:7}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[dr] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[dl] \arrow[r] & \dots \arrow[dll] \\
                & n 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}
        \\ % new row
        \\

        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:8}
            \begin{tikzcd}[row sep=small, column sep=small]
                f_0 \arrow[r] \arrow[d] & f_1 \arrow[r] \arrow[d] & f_2 \arrow[r] \arrow[d] & \dots \arrow[d] \\
                n_0  & n_1  & n_2 & \dots 
            \end{tikzcd} \\
            \end{counterexample}
        \end{minipage}

        &
        \begin{minipage}{0.3\textwidth}
            \centering
            \begin{counterexample}\label{CE:9}
            \begin{tikzcd}[row sep=small, column sep=small]
                a \arrow[r, bend left] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % \\ % New row
    % \\
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:10}
            \begin{tikzcd}[row sep=small, column sep=small]
                d  \arrow[d] \arrow[rr, bend left] & a \arrow[r] \arrow[l]  &  
                b \arrow[r, bend left] & c \arrow[l, bend left] \\  
                f_0 \arrow[r] & f_1 \arrow[r] & f_2 \arrow[r] & \dots  
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    % New row
    \\
    \\
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:11}
            \begin{tikzcd}[row sep=small, column sep=small]
                c \arrow[r, bend left] & b \arrow[l, bend left]  & a \arrow[l] \arrow[r] 
                & d \arrow[r, bend left] & e \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}
    &
    &
    \begin{minipage}{0.3\textwidth}
        \centering
        \begin{counterexample}\label{CE:12}
            \begin{tikzcd}[row sep=small, column sep=small]
                c & a \arrow[r, bend left] \arrow[l] & b \arrow[l, bend left]
            \end{tikzcd} \\
        \end{counterexample}
    \end{minipage}

\end{tabular}
\end{center}

@@

\sacomment{Rewrite the below to reflect changes to the table.}
The tables show a number of changes when moving from properties holding locally to globally. 
Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
globally but not locally.
